Contention Management for 5G

### 2017-05-19 article/article.tex
merge main

      When the period is less than $40000$, the exhaustive search find many more solutions than the greedy algorithm which justifies its use. 
      However for small period, less than $30000$ the computation time is really important and without improvement it would not be possible to tackle 
      larger problems with $10$ to $20$ routes. Moreover, examining the upper bound curve for small periods, we see that there are very few instances
      with a solution for PAZL. It means that with long routes and high load, looking for an affectation without waiting may be too restrictive.
      That is why we present algorithms for the general PALL problem in our next section. We will test them on $8$ long routes and a period between 
      $20000$ and $30000$ where, as we have shown here, there are often no easy to compute affectation without waiting time.

@@

     This algorithm uses the exact same greedy scheduling than LSG. Nevertheless, when it tries to schedule a message that is not able to totally pass $c_t$ before it's deadline (let us call \em{crisis message} this message), the algorithm call a subroutine that reschedule the previous message such that the crisis message will be scheduled earlier.

     \subsubsection{Mix : Simons periodic}

>>>>

      When the period is less than $40000$, the exhaustive search find many more solutions than the greedy algorithms which justifies its use. 
      However for small period, less than $30000$ the computation time is really important and without improvement it would not be possible to tackle 
      larger problems with $10$ to $20$ routes. Moreover, examining the upper bound curve for small periods, we see that there are very few instances
      with a solution for PAZL. It means that with long routes and high load, looking for an affectation without waiting may be too restrictive.
      That is why we present algorithms for the general PALL problem in our next section. We will test them on $8$ long routes and a period between 
      $20000$ and $30000$ where, as we have shown here, there are often no easy to compute affectation without waiting time.

@@

     This algorithm uses the exact same greedy scheduling than LSG. Nevertheless, when it tries to schedule a message that is not able to totally pass $c_t$ before it's deadline (let us call {\em crisis message} this message), the algorithm call a subroutine which, following some criteria, removes some previous messages such that the crisis message can be scheduled earlier.

     If this algorithm gives us a $(P,\tau)$ periodic affectation, it satisfies the criteria $MT({\cal M}) < T_{max}$ Also, the algorithm minimizes $MT({\cal M})$, but does not ensure the periodicity.

     \subsubsection{Final algorithm}

     We adapted the optimal algorithm presented in the previous paragraph, to ensure a periodic $(P,\tau)$ periodic affectation, if it exists, with the given offsets, which are determined by the sending order chose.

    \begin{algorithm}[H]
    \caption{Optimal Periodic}
    \begin{algorithmic}
    \REQUIRE A routage graph ${\cal R_{\cal C}}$,a period $P$, packet size $\tau$, the offsets $m_i$
    \ENSURE $(P-\tau)-$periodic affectation of ${\cal R_{\cal C}}$, if it exists

    \FORALL{route $r_{t_i}$}
    \STATE  $w_i \leftarrow 0$
    \STATE $end-period \leftarrow m_{s_i} + \lambda(r_{s_i}) + t(c_t,r_{t_i}) + P$
    \FORALL{route $r_{t_j}$}
    \STATE $deadline-route \leftarrow m_{s_j} + T_{max}-t(c_s,r_{s_j})$
    \STATE $deadline \leftarrow (deadline-route,end-period)$
    \ENDFOR

    \STATE Call the optimal algorithm

    \ENDFOR

    \STATE return the best $(P-\tau)-$periodic affectation, or FAILURE

    This algorithm runs in $\mathcal{O}(n^3\log{}n)$. It tries for every routes of the routage graph, to fix the first route to comeback, and then determine the deadline of the other routes taking the minimum between the end of the period (determined by the first message that we fixed), and the deadline of the route itself(determined by $m_{s_i} + T_{max}-t(c_s,r_{s_i})$).

    This algorithm guarantee an optimal scheduling for the messages, if it exists, once the offsets $m_i$ has been fixed. The goal is to choose the best starting order, such that we have a good chance to have a $(P,\tau)$ periodic affectation, even with a small period, and T$_{max}$.

    \subsubsection{Results}

    \paragraph{Comparer les departs}

    \paragraph{Comparer les retours}

    \paragraph{Comparer optimal + depart random avec stochastique}
